Verifying Hierarchical Cache Coherence Protocols: a theorem-prover based modular, reusable proof

### 2014-02-04 paper/Background.tex
some modifications of backgrounda

All modern systems have caches between the processor and memory for faster
memory access.  It is often also useful to permit some reorderings of requests
from a processor to the memory to improve performance.  For instance, in the
context of a processor with local store buffer, we may wish to allow a store to
bypass a subsequent load request to a different location. The specification of
which reorderings are permitted or restricted defines the memory consistency
model.

>>>>

All modern systems have caches between the processor and memory for faster
memory access.  It is often also useful to permit some re-orderings of requests
from a processor to the memory to improve performance.  For instance, in the
context of a processor with local store buffer, we may wish to allow a store to
bypass a subsequent load request to a different location. The specification of
which re-orderings are permitted or restricted defines the memory consistency
model.
